---
title: "Data Visualization"
author: "Mikeal Watson"
format: "html"
editor: "visual"
---

### Loading Tidyverse

```{r}
library(tidyverse)
```

I'm starting out by looking at all available data sets in Rstudio.

```{r}
data()
```

```{r}
BOD
```

I've chosen the BOD, which stands for Biochemical Oxygen Demand. I don't have a specific reason for choosing this data. Honestly, it looked like simple data to work with.

I've placed time on the x axis and demand on the y axis. Demand depends on time is how I've thought about it.

```{r}
ggplot(data = BOD,
       mapping = aes(x = Time,
                     y = demand))+
  geom_point()
```

I've now added my points and my line graph.

```{r}
ggplot(data = BOD,
       mapping = aes(x = Time,
                     y = demand))+
  geom_point(size = 4)+
  geom_line(color = "blue")
```

```{r}
ggplot(BOD, aes(Time, demand))+
  geom_point(size = 3)+
  geom_line(color ="blue")
```

```{r}
BOD |>
  ggplot(aes(Time, demand,
             ))+
  geom_point(size = 3)+
  geom_line(color = "blue")
```

I've used the \|\> feature to simply

```{r}
CO2 |>
  ggplot(aes(conc,uptake,
             color = Treatment ))+
  geom_point()
```

```{r}
CO2 |>
  ggplot(aes(conc,uptake,
             color = Treatment ))+
  geom_point(size = 1.5, alpha = .5)+
  geom_smooth(method = lm, se = F)+
  facet_wrap(~Type)+
  labs(title = "CO2 Concetration")+
  theme_bw()
```

```{r}
CO2 |>
  ggplot(aes(Treatment, uptake))+
  geom_boxplot()+
  geom_point(aes(size = conc,
                 color = Plant))
```

In this graph, I've decided to map inside of the geom_point instead of the top layers of the code, versus my previous graph where I mapped inside of the ggplot chunk.

```{r}
CO2 |>
  ggplot(aes(Treatment, uptake))+
  geom_boxplot()+
  geom_point(alpha = 0.5,
             aes(size = conc,
                 color = Plant))+
  facet_wrap(~Type)+
  coord_flip()+
  theme_dark()+
  labs(title = "Chilled vs Non-Chilled")
```
